Predicting sales of newly published books

### 2015-11-03 paper.tex
Finishing feature selection techniques description. @pacastillo, @jj and @fergunet can review now

For this reason, 
%have been used in this work: BestFirst, that searches the space of feature subsets by greedy hill-climbing augmented with a backtracking facility, and Ranker, that ranks features by their individual evaluations.
\end{itemize}

>>>>

For this reason, the search method used with CFS has been BestFirst, that searches the space of feature subsets by greedy hill-climbing augmented with a backtracking facility. On the other hand, Ranker is the searching criteria used with the Relief evaluator. This method ranks features by their individual evaluations.
\end{itemize}

Finally, Section \ref{sec:experiments} provides a comparison between the feature reduction through SOM, and the feature selection techniques that have been described.
